---
title: "Homework 5"
author: "Chong Li"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
library(readxl)
library(tidyverse)
library(dplyr)
library(knitr)
```

# Problem 1
The raw data describes the victim characteristics of murder cases (name/race/age/sex), the location where the murders took place (state/city/lat/lon), the identifiers of the cases and the reported date, and lastly, the disposition of the case (close or open/arrest or no arrest)
```{r}
# Read in the csv file and add the city_state variable, as well as variable for open/no arrest
homicide_df = read.csv("./homicide-data.csv") %>%
  janitor::clean_names() %>%
  mutate(city_state = str_c(city,state,sep=",")) %>% 
  relocate(city_state, .before=lat)  %>%
  mutate(unsolved = (grepl("Closed without arrest",disposition,ignore.case=TRUE) |
                       grepl("Open/No arrest",disposition,ignore.case=TRUE)))

head(homicide_df) %>% kable()

# count the total number of murder cases as well as unsolved murder cases
cases_df = homicide_df %>%
  count(city_state,name = "cases")

unsolved_df = homicide_df %>%
  filter(unsolved == TRUE) %>%
  count(city_state,name = "unsolved_cases")

sum_df = merge(cases_df,unsolved_df,by.x="city_state",by.y="city_state")

head(sum_df) %>% kable()

# for the city of Baltimore, use prop.test function to estimate unsolved cases
baltimore = sum_df %>% filter(city_state=="Baltimore,MD")
baltimore_prop = prop.test(baltimore$unsolved_cases,baltimore$cases) %>% 
  broom::tidy() %>% 
  select(estimate,conf.low,conf.high)

signif(baltimore_prop,3) %>% kable()

# run prop.test for each cities in the dataset
all_prop = sum_df %>%
  mutate(
    prop_test = map2(.x = unsolved_cases, .y = cases, ~prop.test(.x,.y)),
    prop_test_tidy = map(.x = prop_test, ~broom::tidy(.x))
  ) %>%
  select(city_state,prop_test_tidy) %>%
  unnest(prop_test_tidy) %>%
  arrange(desc(estimate)) %>%
  select(city_state,estimate,conf.low,conf.high) %>%
  mutate(across(is.numeric, ~ round(., 4)))

head(all_prop) %>% kable()

# create a graph based on the prop.test outputs above

all_prop %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  ggtitle("Proportion of Unsolved Murder Cases") +
  xlab("City") + ylab("Proportion Estimates")


```
  
# Problem 2
```{r}
# create a data frame that consists of all subjects and respective observations
study_df = 
  tibble(file_name = list.files("data")) %>%
  mutate(
    data = map(.x = str_c("./data/", file_name), ~read_csv(.x))
  ) %>%
  unnest(data) %>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observations"
  ) %>%
  mutate(
    arm_id = substr(file_name, 0, 3),group_id = substr(file_name, 5, 6)) %>%
  mutate(
      arm_id = case_when(
        arm_id == "con" ~ "control",
        arm_id == "exp" ~ "experiment"
      ),
      week = substr(week,6,6)
  ) %>%
  relocate(group_id,.before=week)%>%
  relocate(arm_id,.before=week) %>%
  select(-file_name)

# create a spaghetti plot showing observations on each subject
study_df %>%
  ggplot(aes(x = week, y = observations, group = group_id, color = group_id)) +
  geom_line() + facet_grid(~arm_id) +
  ylab("Observations") + xlab("Week") 

```
  
From the graph, it is clear that the experimental group shows a strong positive trend over the 8-week observation period while the control group had a flat trend despite having fairly large flutuation in observation values.


